Deployable Probabilistic Programming

### 2019-04-23 paper/paper.tex
work in progress

\begin{table*}
\begin{tabular}{r | c |  c | c | c | c | c |}
	{\it model}  & \multicolumn{4}{c|}{\it time} & \multicolumn{2}{c|}{} \\
	& \multicolumn{2}{c|}{\it compilation} & \multicolumn{2}{c|}{\it execution} & \multicolumn{2}{c|}{\it memory} \\
	& Infergo & Stan & Infergo & Stan & Infergo & Stan \\\hline
	8 schools & 0.15s & 10s & 0.6s & 0.3s & 5.5MB & 16MB \\
	10D normal, 100 points & 0.15s & 10s & 3.0s & 2.0s & 5.7MB & 20 MB \\
	50D normal, 100 points & 0.15s & 10s & 13.0s & 4.0s & 5.8MB & 22 MB  
\end{tabular}
\caption{Memory and running times for 1000 iterations of HMC with 10 leapfrog steps.}
\label{tab:memory-runtime}
\end{table*}

>>>>

\begin{table*}
\begin{tabular}{r | c |  c | c | c | c | c | }
	{\it model}  & \multicolumn{6}{c|}{\it time} \\
	& \multicolumn{3}{c|}{\it compilation} & \multicolumn{3}{c|}{\it execution} \\
	& Infergo & Turing & Stan & Infergo & Turing & Stan \\\hline
	8 schools              & 0.5s & & & 0.6s  & & \\
	10D normal, 100 points & 0.5s & & & 3.0s  & & \\
	50D normal, 100 points & 0.5s & & & 13.0s & & \\
	LDA, 262 words, 25 docs
	                       & 0.6s & & &       & & 
\end{tabular}
\caption{Compilation and execution times for 1000 iterations 
	of HMC with 10 leapfrog steps.}
\label{tab:memory-runtime}
\end{table*}
